### 2022-01-14 manuscript/manuscript.Rmd
Update manuscript.Rmd

---
title             : "Avenues for critical discourse at influential scientific journals: A cross-disciplinary assessment of post-publication peer review policies and practice"
shorttitle        : "Post-publication peer review"

@@

abstract: |
  Critical scrutiny of published research is an important feature of a self-correcting scientific ecosystem. Academic journals exert considerable control over criticism submitted in the form of letters, commentaries, or online comments (post-publication peer review, PPPR). Currently, there is limited empirical data documenting how journals handle PPPR. We assessed PPPR policies and practice amongst 330 influential journals operating across 22 scientific disciplines. 123 (37%) journals did not offer any options for submitting PPPR. 207 (63%) journals offered PPPR options, but often imposed limits on length (median 1000, IQR 700 words) and time-to-submit (median 12, IQR 22 weeks). The most restrictive limits were 175 words and 2 weeks; the least restrictive PPPRs had no limits. Of a random sample of 2066 research articles published in 2018 by PPPR-offering journals, we found that 1.9% (95% CI [1.4, 2.6]) were the subject of at least one PPPR. Examination of 58 PPPRs found, for example, that 44 received an author reply, of which 41 asserted that the authors’ conclusions were unchanged. Clinical Medicine stood out as the domain with the most active PPPR culture, with all 15 journals providing PPPR options and publishing the most PPPR, but also imposing the strictest length limits (median 400, IQR 150 words) and time-to-submit limits (median 4, IQR 2 weeks). Overall, our findings suggest that influential academic journals often pose serious barriers to the cultivation, documentation, and dissemination of PPPR. We suggest policies that journals could adopt to promote a richer culture of post-publication critique.

@@

After Study One, but before beginning Study Two, we decided to also compute a secondary (not preregistered) PPPR prevalence estimate based on how many of randomly sampled articles were themselves examples of PPPR. To align the two estimates, we only used the first 10 eligible articles for each journal, and therefore the total number of assessed articles was 2066 as above. These two prevalence measures have complementary strengths and limitations. For the primary prevalence estimate PPPR was identified through searches of article web pages for linked PPPR. Its accuracy therefore depends on journals actively and visibly linking to PPPR on their webpages. However, it is not dependent on PPPR being indexed in Web of Science databases. By contrast, for the secondary prevalence estimate PPPR was identified by checking if sampled articles were themselves examples of PPPR. Thus, it does not rely on journals linking to relevant PPPR, but it does rely on PPPR being indexed in Web of Science databases, because that is how the sampled articles were identified. Note that our primary estimate was also time-restricted in the sense that any identified PPPR must have been published after 2018 (when the sampled articles were published. By contrast, our secondary estimate could theoretically detect PPPRs pertaining to any previously target articles, regardless of their publication date.

>>>>

---
title             : "A cross-disciplinary assessment of post-publication peer review policies and practice in influential scientific journals."
shorttitle        : "Post-publication peer review"

@@

abstract: |
  Critical scrutiny of published research is an important feature of a self-correcting scientific ecosystem. Academic journals exert considerable control over criticism submitted in the form of letters, commentaries, or online comments (post-publication peer review, PPPR). Currently, there is limited empirical data documenting how journals handle PPPR. We assessed PPPR policies and practice amongst 330 influential journals operating across 22 scientific disciplines. 123 (37%) journals did not offer any options for submitting PPPR. 207 (63%) journals offered PPPR options, but often imposed limits on length (median 1000, IQR 700 words) and time-to-submit (median 12, IQR 22 weeks). The most restrictive limits were 175 words and 2 weeks; the least restrictive PPPRs had no limits. Of a random sample of 2066 research articles published in 2018 by PPPR-offering journals, we found that 1.9% (95% CI [1.4, 2.6]) were the subject of at least one PPPR. We examined 58 PPPRs and found, for example, that 44 received an author reply, of which 41 asserted that the authors’ conclusions were unchanged. Clinical Medicine stood out as the domain with the most active PPPR culture, with all 15 journals providing PPPR options and publishing the most PPPR, but also imposing the strictest length limits (median 400, IQR 150 words) and time-to-submit limits (median 4, IQR 2 weeks). Overall, our findings suggest that influential academic journals often pose serious barriers to the cultivation, documentation, and dissemination of PPPR. We suggest policies that journals could adopt to promote a richer culture of post-publication critique.

@@

After Study One, but before beginning Study Two, we decided to also compute a secondary (not preregistered) PPPR prevalence estimate based on how many of randomly sampled articles were themselves examples of PPPR. To align the two estimates, we only used the first 10 eligible articles for each journal, and therefore the total number of assessed articles was 2066 as above. These two prevalence measures have complementary strengths and limitations. For the primary prevalence estimate PPPR was identified through searches of article web pages for linked PPPR. Its accuracy therefore depends on journals actively and visibly linking to PPPR on their webpages. However, it is not dependent on PPPR being indexed in Web of Science databases. By contrast, for the secondary prevalence estimate PPPR was identified by checking if sampled articles were themselves examples of PPPR. Thus, it does not rely on journals linking to relevant PPPR, but it does rely on PPPR being indexed in Web of Science databases, because that is how the sampled articles were identified. Note that our primary estimate was also time-restricted in the sense that any identified PPPR must have been published after 2018 (when the sampled articles were published). By contrast, our secondary estimate could theoretically detect PPPRs pertaining to any previously target articles, regardless of their publication date.
